Visualization of [fulle name] Fractional Integrals

### 2019-03-26 fractional/CMJ style files/article-template.tex
new sentences

%\item[\biogpic{\includegraphics[width=84pt]{Herbert_Hoover.pdf}}Herbert Hoover] (hchoover@stanford.edu) entered Stanford University in 1891, after failing all of the entrance exams except mathematics.  He received his BS degree in geology in 1895, spent time as a mining engineer, then was appointed by his co-author to the U.S. Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
%\end{biog}

The idea of integer-order differentiation and integration is well known to most undergraduates. However, undergraduates are less familiar with the idea of an arbitrary order differential or integral (i.e. fractional-order calculus).
Even though most undergraduates have a limited understanding of fractional-order calculus they generally are quite interested in the subject. This is quite 
evident from perusing mathematical social media platforms and from surveying articles published in undergraduate journals []. The reason fractional calsulus is not generally 
taught at the undegraduate level is partly due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. This paper 
is specifically written for undergraduate lecturers and is very pedigogical in nature. In this paper we present a novel geometric interpretation of the 
Riemann-Liouville fractional integral which is similar in nature to the classical interpretation of classical integration. Our hope is that this 
geometric interpretation will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.

This is not to say that there  This is partly, because there is no simplistic geometric interpretation for fractional calculus.

It can be argued that fractional-order calculus is as old as classical calculus itself. Leibniz, who is regarded by many scholars as the farther of calculus, invented the following notation: $\frac{d^n y}{d x^n}$. Leibniz mentiones the notion of a fractional 
order derivative in a letter he sent to L'Hospital. In this letter he is responding to a question L'Hospital posed. L'Hospital asked the question: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. He responded, quite prophetically, ``\emph{This is an apparant paradox from which, one day, useful 
consequences will be drawn}.'' Liouville and Riemann laid much of the groundwork which was needed to define the Riemann-Liouville fractional integral [Laurent’].

It was pointed out at the first international conference on fractional calculus in New Haven (USA) in 1974 that literature lacked an acceptable geometric and physical
interpretation of the fractional integral and that this has been the case for more than 300 years []. Consequently the last few decades has seen a number of papers that attempt to rectify this. There now exists probabilistic interpretations, 
geometric interpretations and ecenomic interpretations of the fractional integral.

>>>>

%\item[\biogpic{\includegraphics[width=84pt]{Herbert_Hoover.pdf}}Herbert Hoover] (hchoover@stanford.edu) entered Stanford University in 1891, after failing all of the entrance exams except mathematics.  He received his BS degree in geology in 1895, spent time as a mining engineer, then was appointed by his co-author to the U.S. Food Administration and the Supreme Economic Council, where he orchestrated the greatest famine relief efforts of all time.
%\end{biog}
%This is not to say that there  This is partly, because there is no simplistic geometric interpretation for fractional calculus.  
\noindent
Fractional-order calculus can be summarized as the generalization of integer-order differentials and integrals to an arbitrary order. It can be argued that 
fractional-order calculus is as old as classical calculus itself. Leibniz, who is regarded by many scholars as the farther of calculus, invented the following notation: $\frac{d^n y}{d x^n}$. Leibniz mentiones the notion of a fractional 
order derivative in a letter he sent to L'Hospital. In this letter he answers the following question posed by L'Hospital: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. He responded, quite prophetically, ``\emph{This is an apparant paradox from which, one day, useful 
consequences will be drawn}.'' In this paper, we will mainly focus our attention on fractional-order integration and in particular investigate the Riemann-Liouville fractional 
integral. It is Liouville and Riemann who laid much of the groundwork which was needed to define what is now known as the Riemann-Liouville fractional integral [Laurent’].

It was pointed out at the first international conference on fractional calculus in New Haven (USA) in 1974 that literature lacked an acceptable geometric and physical
interpretation of the fractional integral. In 1974, this had been the state of affairs for more than 300 years []. Subsequently, the last few decades has seen a number of papers that attempt to rectify this. There now exists probabilistic interpretations, 
geometric interpretations and ecenomic interpretations of the fractional integral.

The idea of integer-order differentiation and integration is well known to most undergraduates. However, undergraduates are less familiar with the idea of an arbitrary order differential or integral (i.e. fractional-order calculus).
Even though most undergraduates have a limited understanding of fractional-order calculus they generally are quite interested in the subject. This is quite 
evident from perusing mathematical social media platforms and from surveying articles published in undergraduate journals []. One of the reason fractional calculus is not generally 
taught at the undegraduate level is due to the fact that the notion is quite abstract and it is therefore difficult to interpret geometrically. In this paper adress this shortcomming by presenting  
a novel geometric interpretation of the Riemann-Liouville fractional integral which is similar in nature to the classical interpretation of classical integration. Our hope is that this 
geometric interpretation will encourage and enable undergraduate lectures to introduce undergraduates to this fascinating mathematical discipline.
